\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}

% Define colors
\definecolor{techblue}{RGB}{0, 122, 204}
\definecolor{darkgray}{RGB}{50, 50, 50}

\title{\textbf{Software Requirements Specification (SRS) \\ Serenify Mental Health Platform}}
\author{SALVIORIS Development Team}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
\subsection{Purpose}
This document specifies the software requirements for the Serenify Mental Health Platform. It provides a comprehensive overview of the system's functional and non-functional requirements, technology stack, and architectural design.

\subsection{Scope}
Serenify is a web-based application designed to facilitate anonymous emotional support, journaling, and professional therapy connections. The system consists of a Go-based backend API and a Next.js frontend application.

\section{Technology Stack}

\subsection{Frontend Environment}
\begin{itemize}
    \item \textbf{Framework}: Next.js 15 (App Router)
    \item \textbf{Library}: React 19
    \item \textbf{Language}: TypeScript
    \item \textbf{Styling}: Tailwind CSS, Sass
    \item \textbf{UI Components}: Radix UI, Lucide React
    \item \textbf{State Management}: React Context API, Hooks
    \item \textbf{Form Handling}: React Hook Form, Zod
\end{itemize}

\subsection{Backend Environment}
\begin{itemize}
    \item \textbf{Language}: Go (Golang) 1.25+
    \item \textbf{Router}: Chi v5
    \item \textbf{API Style}: RESTful
    \item \textbf{Authentication}: JWT (JSON Web Tokens)
    \item \textbf{Password Security}: Argon2
    \item \textbf{Media Management}: Cloudinary
\end{itemize}

\subsection{Data Persistence}
\begin{itemize}
    \item \textbf{Relational Database}: PostgreSQL (User accounts, Group metadata, Audit logs)
    \item \textbf{NoSQL Database}: MongoDB (Vents, Journals, Chat history, Therapist profiles)
    \item \textbf{Cache Layer}: Redis (Sessions, Rate limiting, Real-time messaging)
\end{itemize}

\section{Functional Requirements}

\subsection{User Management}
\begin{itemize}
    \item \textbf{FR-1}: Users shall be able to register and log in securely.
    \item \textbf{FR-2}: The system shall support account recovery via encrypted email/phone data.
    \item \textbf{FR-3}: Therapists shall be able to apply for professional accounts with credential uploads.
    \item \textbf{FR-4}: Administrators shall be able to approve or reject therapist applications.
\end{itemize}

\subsection{Content \& Interaction}
\begin{itemize}
    \item \textbf{FR-5}: Users shall be able to post anonymous emotional vents.
    \item \textbf{FR-6}: Users shall be able to maintain a private, encrypted personal journal.
    \item \textbf{FR-7}: The system shall support real-time chat groups with message persistence.
    \item \textbf{FR-8}: Users shall be able to search and view verified therapist profiles.
\end{itemize}

\section{Non-Functional Requirements}

\subsection{Performance}
\begin{itemize}
    \item \textbf{NFR-1}: The system shall respond to API requests within 200ms on average.
    \item \textbf{NFR-2}: Frontend pages shall load in under 2 seconds using Next.js optimizations.
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item \textbf{NFR-3}: All user passwords must be hashed using the Argon2 algorithm.
    \item \textbf{NFR-4}: Sensitive data must be encrypted at rest and in transit (TLS/SSL).
    \item \textbf{NFR-5}: API rate limiting must be enforced to prevent brute-force attacks.
\end{itemize}

\subsection{Scalability}
\begin{itemize}
    \item \textbf{NFR-6}: The system must support horizontal scaling of the backend services.
    \item \textbf{NFR-7}: The NoSQL database (MongoDB) must handle high-volume write operations for chat and vents.
\end{itemize}

\section{System Architecture}
The system follows a \textbf{Clean Architecture} pattern on the backend and a \textbf{Component-Based Architecture} on the frontend. Communication between the two is facilitated through a RESTful API and WebSockets for real-time features.

\end{document}
